A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-23 sections/Appendix.tex
Translation table: paper symbol to Abella relation

>>>>

\subsection{Translation Table for the Proof Scripts}
In the proof scripts, we use textual relational definitions
rather than the symbolic ones used in the paper.
The mapping should be helpful for anyone who reads the script.

\afterpage{%
\clearpage% Flush earlier floats (otherwise order might not be correct)
\begin{landscape}% Landscape page

\begin{figure}[ht]
\centering
\begin{tabular}{c|c|c|c}
Symbol & Abella textual relation & File (.thm) & Description\\\hline
\hline
$A$    & {\tt ty, wft, wfta} & typing &
    The "type" type, decl./alg. well-formedness\\\hline
$e$    & {\tt tm, wftm} & typing &
    The "term" type, (alg.) well-formedness\\\hline
$\Psi, \Gm$ & {\tt olist, wfj} & typing &
    {\tt olist} is Abella's built-in list type, i.e. {\tt [o]}\\\hline
$\jg$  & {\tt judgment, wfjg} & typing &
    Judgment chain and its well-formedness\\\hline
\hline
$\Gm\rto\Gm'$ & {\tt reduction} & smallStep &
    Algorithmic reduction: paper version\\\hline
$\Gm\redto\nil$ & {\tt judge} & typing &
    ({\tt judge} $\Gm$): a success reduction on $\Gm$\\\hline
\hline
$\Gm \sto \Om$ & {\tt tex} & trans &
    "transfer existential variables"\\\hline
$\Om\redto\nil$ & {\tt dc, dcl} & trans, dcl &
    Declarative chain representation\\\hline
\hline
$\Psi'\le\Psi$ & {\tt esub} & declTyping & Declarative context subtyping\\\hline
\hline
$\Gm\jExt\Gm'$ & {\tt jExt} & inst\_decidable & "Judgment extension"\\\hline
$\Gm_i$ & {\tt iexp} & inst\_decidable & instantiation judgments ($\Gm \vdash_{wf} \Gm_i$)\\\hline
$\Gm_\le$ & {\tt subExp} & inst\_decidable & subtyping judgments\\\hline
\hline
$|\cdot|_e$ & {\tt tmSize, tmSizeJ, tmSizel} & declTyping, decidability &
    Size measure for term, judgment chain or context\\\hline
$|\cdot|_\Leftrightarrow$ & {\tt m\_judgeJ, m\_judge} & decidability &
    Judgment measure for judgment chain or context\\\hline
$|\cdot|_{\al}$ & {\tt nVar} & inst\_decidable &
    Existential measure for context\\\hline
$|\cdot|_\forall$ & {\tt order, orderJ, orderl} & order, inst\_decidable &
    Polymorphism measure for type, judgment chain or context\\\hline
$|\cdot|_\to$ & {\tt depth, depthJ, depthl} & order, decidability &
    Function measure for type, judgment chain or context\\\hline
\end{tabular}
\caption{Translation Table for the Proof Scripts}
\label{fig:translation_table}
\end{figure}

\end{landscape}
\clearpage% Flush page
}
